Draft

### 2017-09-03 Thesis/Draft.tex
Add corollary for lower bound

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{hyperref}
\usepackage[lined,boxed]{algorithm2e}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}
\newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%

@@

When introducing the thresholding bandit setting, we did not mention the
fact that the budget \(T\) does not need to be fixed upfront. Indeed,
the setting in which the budget is \emph{not} fixed upfront might be
more popular among the best arm identification and top-\(m\) literature.
This setting is called \emph{fixed-confidence}, while the setting we
considered so far is called \emph{fixed-budget}. In the fixed-budget
setting, we run algorithms for \(T\) samples and then compare them based
on their expected loss,
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which holds for every
problem \(\nu \in \mathcal{M}_m\) that the classification holds at least
with confidence level \(1-\delta\), that is,
\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
strategy has to achieve this level of confidence in its prediction
before it is allowed to stop sampling. This is the fixed-confidence
case, in which the budget \(T\) is no longer fixed upfront, but becomes
a random variable. We compare algorithms by their expected number of
draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and prefer those which arrive at
the confidence level \(1-\delta\) with a smaller expected budget.

@@

To prove this statement, we assume as before that the arms are ordered
by their means decreasing in size. For a given \(\delta\)-PAC algorithm
\(\mathcal{A} = ((A_t), \tau, \hat{S}_m)\), and under the continuity
conditions (compare Kaufmann et al. (2016)), there exists for every arm
\(a \in \{1, \dots, K\}\) an alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, only arm \(a\) is modified in accordance with
the continuity conditions. Modified in such a way, the arm \(\nu_{m+1}\)
is now closer to \(\nu_a\) as measured by the Kullback-Leibler
divergence than \(\nu_a'\) is to \(\nu_a\), if \(\mu_a > \mu_{m+1}\)
(consequently, \(\mu_a' < \mu_{m+1}\)). On the other hand, if
\(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away from \(\nu_a\)
just enough so that \(\nu_a\) is closer to \(\nu_m\) than to \(\nu_a'\)
(consequently, \(\mu_a' > \mu_m\)). These changes in distribution make
the original set of optimal arms, \(\{1,\dots,m\}\), no longer optimal
under the alternative model \(\nu'\). Given that the algorithm returns
\(\hat{S}_m\), we know that for the event
\(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element of the
\(\sigma\)-Algebra \(\mathcal{F}_{\tau}\) induced by the stopping time
\(\tau\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!).

To now give the lower bound on the expected number of samples,
\(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given by the
authors for such changes in distribution in bandit models.

@@

\begin{equation*}
\mathbb{E}_{\nu}[\tau] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

Given that we will be naturally interested in either very high or very
low confidence of our algorithm, that is, \(P_\nu(\mathcal{E})\) is
either close to 0 or 1, it is possible to use the following
approximation to the binary relative entropy:

\begin{equation}\label{bre_approx}
\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}
\end{equation}

And so the final lower bound can be written as

\begin{equation*}
\mathbb{E}_{\nu}[\tau] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-1-1.pdf}

Given this general lower bound for the sampling complexity, or expected
number of draws, it makes sense to define the complexity of a Top-\(m\)
bandit problem using the Kullback-Leibler divergence. After all, besides
the number of arms and the experimenter-chosen confidence, it is just
how close arms are with respect to each other in terms of
Kullback-Leibler divergence that influences the sampling complexity.

Thus, following Kaufmann et al. (2016), define the complexity
\(\kappa_C(\nu)\) for the fixed confidence setting as

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[\tau_{\delta}]}{\log \frac{1}{\delta}}.
\end{equation}

By plugging in the lower bound on the sampling complexity, we arrive at
a complexity measure that depends only on the Kullback-Leibler measuring
for each arm how far it is away from the border between the two groups
of arms. To see this, consider the lower bound on the complexity measure
given in Kaufmann et al. (2016):

@@

Given this description, we can already note that an intuitive extension
of this complexity notion to the thresholding bandit problem might
involve replacing \(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual
threshold \(\tau\) (notation in Locatelli et al.) that divides the group
above the threshold from the group below the threshold. In this sense,
the previously used \(\alpha\) is similar to the \(\epsilon\) used in
Locatelli et al. (2016).

Before we get to an extension of the thresholding bandit problem,
however, at least two important steps remain. First, we need to define a
complexity for the fixed budget problem. Second, we need to create
algorithms that can match the lower bound.

Kaufmann et al. are able to provide a bound on their complexity measure
in the fixed budget case, however only in the case of \textbf{two-armed}
bandit models. As demanded in their paper, a fixed-budget algorithm is
called consistent if the failure probability
\(p_t(\nu) := \mathbb{P}_{\nu}(\hat{S}_m \neq S^*_m)\) tends to zero as
the number of samples goes to infinity. Also, define the complexity in
the fixed-budget setting as follows:

@@

Given this definition, one can interpret the bound given in Theorem 12
of Kaufmann et al. directly as a lower bound on the complexity
\(\kappa_B(\nu)\) (note the inverse).

\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed-budget setting, any consistent algorithm satisfies:

@@

For a proof, consider first the two different bandit models, \(\nu\) and
\(\nu'\), where we fix without loss of generality that \(a^* = 1\) is
the best arm in \(\nu\), while \(a^* = 2\) in \(\nu'\). Note that in
this case we don't necessarily try to fool the algorithm by a change of
distribution. Indeed, we want the algorithm \(\mathcal{A}\) to be
consistent for both problems. Since we are in the fixed-budget setting,
the stopping time is fixed at \(\tau = t\). Even though the correct
decision differs between the two problems, we focus on the event
\(A = (\hat{S}_1 = 1)\). Given the formulation in Kaufmann et al.
(2016), we have \(A \in \mathcal{F}_t = \mathcal{F}_{\tau}\). Now, we
can apply Lemma 1 as before, as it in essense gives a measure of how
different two bandit models are. Here, we want to know how different
\(\nu\) is from \(\nu'\), and so, given we have only two arms,

@@

The expectations were chosen with respect to \(\nu'\) in order to allow
the for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\)
and \(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in
\(\nu'\)). But since algorithm \(\mathcal{A}\) is consistent for both
\(\nu\) and \(\nu'\), we know that there should exist some number of
samples such that the probability of event \(A\) is bigger in setting
\(\nu\) (where it is the correct decision), than in setting \(\nu'\)
(where this would be a wrong decision and failure). Thus, for every
\(\epsilon > 0\), there exists \(t_0(\epsilon)\) such that for all
\(t \geq t_0(\epsilon)\),
\(\mathbb{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\). Consequently,
if we plug in the bound of \(\epsilon\) for \(\mathbb{P}_{\nu'}(A)\),
then

@@

\textbf{Mention something about the fact that we were not able to do
this for more than 2 arms and top-m bandits. How could it be extended to
that? How could it be extended to the threshold bandit?}

As noted by Kaufmann et al. (2016), the advantage of this lower bound is
that it makes the complexity in the fixed-confidence and the
fixed-budget setting directly comparable. The disadvantage of course
being that the result only holds for two-armed models. While the authors
were not able to derive directly comparable lower bounds for the
Top-\(m\) case, they did derive a first lower bound in the Gaussian case
with equal variances. While we would like to move beyond Gaussian
distributions in the work at hand, the idea for the proof might show a
way of how the ideas can be transferred to the thresholding bandit
problem. We first state the result and then discuss the proof.

\begin{lemma}[Lemma 15, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlLemma15}
Let $\nu$ and $\nu'$ be two bandit models such that $S^*_m(\nu) \neq S*_m(\nu')$. Then

\begin{equation*}
H +(\nu) = \sum_{a=1}^m \frac{2\sigma^2}{(\mu_a - \mu_{m+1})^2}, \quad H^-(\nu) = \sum_{a=m+1}^K \frac{2\sigma^2}{(\mu_m - \mu_a)^2} \quad
and \quad
H(\nu) = H^+(\nu) + H^-(\nu).
\end{equation*}

There exists $a \in {1, \dots, m}$ and $b \in \{m+1, \dots, K\}$ such that the bandit model $\nu^{[a,b]}$ described in Figure 4 (Kaufmann et al., 2016) satisfies $H(\nu^{[a,b]}) < H(\nu)$ and is such that

Given that we are again in the Top-\(m\) setting, the proof idea is
similar to the proof of Theorem \ref{theorem:KaufmannEtAlTheorem4} in
that we again consider problems where we switch arms around the limit
seperating the two groups of arms as given implicitly by \(\mu_{[m]}\)
and \(\mu_{[m+1]}\). The hope here being that these methods could be
applied to the thresholding bandit problem where the threshold of course
gives the limit between the arms above and below the threshold. As we
have seen in chapter 1, this flip around the threshold was of course
used in the proof of the lower bound in Theorem 1 of Locatelli et al.
(2016). However, there, again, the distributions were assumed to be
Gaussian. This brings the big advantage that the Kullback-Leibler
divergence becomes symmetric, and the feedback can take values on all
\(\mathbb{R}\). And by using the complexity measure \(H(\nu)\), it is
also clear that there exists an arm that is undersampled with respect to
its contribution to the overall complexity of the problem (or sampled
exactly according to its contribution), which leads to a convenient
upper bound on this arms number of draws which is again employed in both
the proof of Theorem \ref{theorem:KaufmannEtAlTheorem17} and in
Locatelli et al. (2016). It is not clear yet, whether the same can also
be done with other complexity measures.

We do not repeat the proof here for now.

See p20!

What remains is to present algorithms that are able to match the lower
bounds derived so far.

@@

Given these lower bounds, all that is left is to find algorithms which
are able to match the complexity. Sadly, not straightforward for
Bernoullis.

Kaufmann et al. (2016) do not present algorithms matching the lower
bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
and Theorem \ref{theorem:KaufmannEtAlTheorem12}.

Given that Locatelli et al. (2016), and thus the problem we mostly
consider in this thesis, is in the fixed-budget setting, we are most
interested in the matching strategies for Theorem
\ref{theorem:KaufmannEtAlTheorem12}. However, given that the lower bound
applies only to two-armed bandits, the algorithms are of limited
practical interest. Furthermore, the algorithms proposed require
knowledge that is in general not available upfront.

For the example of Gaussian distributions, the knowledge of the
(potentially different) variance is assumed which enables a strategy
that pulls each arm proportional to its variance.

Even worse is the case of Bernoulli two-armed bandit models where the
proposed algorithm requires knowledge about the true parameters of the
distributions. That this limits the practical interest is also noted by
the authors of Kaufmann et al. (2016). Thus, they suggest to use uniform
sampling strategies in the case of two-armed Bernoulli bandits, and show
that there is not much to be lost by doing so.

Thus, Kaufmann et al. (2016) join a number of other papers like Audibert
et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
find matching strategies in the fixed-budget setting that do not rely on
knowledge of parameters or the complexity of the problem.

In contrast, Kaufmann et al. (2016) are able to show that their
complexity measure derived for the fixed-confidence setting,
\(\kappa_C(\nu)\), can be upper-bounded using the upper bound of the
sample complexity (number of pulls) given for the KL-LUCB algorithm in
Kaufmann and Kalyanakrishnan (2013). Consequently, in the case of
exponential family bandits, the complexity \(\kappa_C(\nu)\) is bounded
as given in equation (6) in Kaufmann et al. (2016):

@@

\subsection{Optimal Best Arm
Identification}\label{optimal-best-arm-identification}

A very similar application of the KL divergence has been given in
Garivier and Kaufmann (2016) to derive a lower bound on the sample
complexity in the case of best arm identification. In particular, the
transportation Lemma 1 is used again. And a matching algorithm for
\(K \geq 2\) arms is proposed.

Talk about: - Not a simple sum of squares - Idea of algorithm: Equalize
the probability of all wrong decisions

In Garivier and Kaufmann (2016), the authors are able to derive a
somewhat similar lower bound on the sample complexity of a \(K\)-armed
bandit in the single best arm identification problem with fixed
confidence. Additionally, they provide a \(\delta\)-PAC algorithm
achieving said bound asymptotically.

In particular, the authors pick up Lemma 1 from Kaufmann et al. (2016)
-- which we discussed above -- to derive the lower bound. While
presenting these results, we try to stick as much as possible with the
notation used so far. In particular, we let for distributions
\(\nu_{\theta}\) from a canonical exponential family, which can be
parameterized by its mean \(\stackrel{.}{b}(\theta) = \mu\) and thus be
written as \(\nu^{\mu}\); for these, we continue to write the
Kullback-Leibler divergence as

\begin{equation*}
\KL(\mu, \mu') = \KL(\nu^{\mu},\nu^{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu')
\end{equation*}

while \(d(x,y)\) continues to represent the binary relative entropy.

As we will consider only problems with exponential family distributions,
the distributions can be parameterized by their means. Therefore, if we
let \(\mathcal{S}\) to be a set of bandit models with \(K\)
distributions each, then each model is fully defined by a vector
\(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
\(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
\(a^*(\bm{\mu})\) such that
\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
confidence, we specify the risk \(\delta\). The strategies corresponding
to this risk are called \(\delta\)-PAC if for every
\(\bm{\mu} \in \mathcal{S}\),
\(\mathbb{P}_{\bm{\mu}}(\tau_{\delta} < \infty) = 1\) (the strategy ends
surely after a finite number of samples) and
\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{\tau_{\delta}} \neq a^*) \leq \delta\)
(the probability of picking not the optimal arm is smaller than the
fixed risk). As in Garivier and Kaufmann (2016), we introduce the set of
problems for which the optimal arm is different from the one in
\(\bm{\mu}\):

@@

where \(\bm{\lambda}\) is the vector of means defining the distributions
of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
probability distributions on the arms \(\mathcal{A}\):
\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). We are
now ready to state the theorem.

@@

\begin{equation*}
\mathbb{E}_{\bm{\mu}} [\tau_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
\end{equation*}

@@

@@

>>>>

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{hyperref}
\usepackage[lined,boxed]{algorithm2e}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}
\newcommand*{\Alignyesnumber}{\refstepcounter{equation}\tag{\theequation}}%

@@

When introducing the thresholding bandit setting, we did not mention the
fact that the budget \(T\) does not need to be fixed upfront. Indeed,
the setting in which the budget is \emph{not} fixed upfront might be
more popular among the best arm identification and top-\(m\) literature.
This setting is called \emph{fixed confidence}, while the setting we
considered so far is called \emph{fixed budget}. In the fixed budget
setting, we run algorithms for \(T\) samples and then compare them based
on their expected loss,
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}(\mathcal{S}^*_m \neq \hat{\mathcal{S}}_m) =: p_t(\nu)\)
as we have seen in \(\autoref{sec:Setup}\). Alternatively, consider a
\(\delta\)-PAC strategy \(\mathcal{A}(\delta)\)for which holds for every
problem \(\nu \in \mathcal{M}_m\) that the classification holds at least
with confidence level \(1-\delta\), that is,
\(\mathbb{P}(\mathcal{S}^*_m = \hat{\mathcal{S}}_m) \geq 1-\delta\). The
strategy has to achieve this level of confidence in its prediction
before it is allowed to stop sampling. This is the fixed confidence
case, in which the budget \(T\) is no longer fixed upfront, but becomes
a random variable. We compare algorithms by their expected number of
draws \(\mathbb{E}_{\nu}[T_{\delta}]\) and prefer those which arrive at
the confidence level \(1-\delta\) with a smaller expected budget.

@@

To prove this statement for a given \(\delta\)-PAC algorithm
\(\mathcal{A}\), we assume certain continuity conditions (compare
Kaufmann et al. (2016)), with which there exists for every arm
\(a \in \{1, \dots, K\}\) an alternative model
\(\nu' = (\nu_1, \dots, \nu_{a-1}, \nu_a', \nu_{a+1}, \dots, \nu_K)\).
In this alternative model, in accordance with the continuity conditions,
only arm \(a\) is modified. After the modification, the arm
\(\nu_{m+1}\) is now closer to \(\nu_a\) as measured by the
Kullback-Leibler divergence than \(\nu_a'\) is to \(\nu_a\), if
\(\mu_a > \mu_{m+1}\) (consequently, \(\mu_a' < \mu_{m+1}\)). On the
other hand, if \(\mu_a < \mu_{m}\), then \(\nu_a'\) will be moved away
from \(\nu_a\) just enough so that \(\nu_a\) is closer to \(\nu_m\) than
to \(\nu_a'\) (consequently, \(\mu_a' > \mu_m\)). These changes in
distribution make the original set of optimal arms, \(\{1,\dots,m\}\),
no longer optimal under the alternative model \(\nu'\). To compare this
to the thresholding bandit problem, assume that arms \(\nu_{m}\) and
\(\nu_{m+1}\) indirectly define a threshold
\(\tau \in (\mu_{m+1},\mu_m)\). Then, by creating an alternative problem
as described here, we flip arm \(a\) around the implied threshold
\(\tau\) (compare the lower bound proof in \autoref{sec:AppendixAPTLB}).

Given that the strategy returns \(\hat{S}_m\), we know that for the
event \(\mathcal{E} = (\hat{S}_m = \{1, \dots, m\})\) (which is element
of the \(\sigma\)-Algebra \(\mathcal{F}_{T}\) induced by the stopping
time \(T\)), that \(\mathbb{P}_{\nu}(\mathcal{E}) \geq 1-\delta\) and
\(\mathbb{P}_{\nu'}(\mathcal{E}) \leq \delta\) (because fixed confidence
\(\delta\)!). To now give the lower bound on the expected number of
samples, \(\mathbb{E}_{\nu}[\tau]\), we employ the general Lemma given
by the authors for such changes in distribution in bandit models.

@@

\begin{equation*}
\mathbb{E}_{\nu}[T] = \sum_{a=1}^K \mathbb{E}_{\nu}[N_a] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \der(1-\delta, \delta)
\end{equation*}

Given that we will be naturally interested in either very high or very
low confidence of our algorithm, that is, \(P_\nu(\mathcal{E})\) is
either close to 0 or 1, it is possible to use the following
approximation to the binary relative entropy given in Kaufmann et al.
(2016):

\begin{equation}\label{bre_approx}
\forall x \in [0,1], \quad \der(x,1-x) = \der(1-x,x) \geq \log \frac{1}{2.4x}.
\end{equation}

This allows us to write the lower bound on the expected stopping time
as:

\begin{equation*}
\mathbb{E}_{\nu}[T] \geq \Big( \sum_{a \in \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m+1]})} + \sum_{a \notin \mathcal{S}_m^*} \frac{1}{\KL(\nu_a, \nu_{[m]})} \Big) \log \big(\frac{1}{2.4\delta} \big).
\end{equation*}

Given this lower bound, it becomes clear that the complexity of the
top-\(m\) problem can be lower bounded by the Kullback-Leibler
divergence between arms and the implied threshold between the \(m\)-th
best arm and the \((m+1)\)-th best arm. After all, the latter gives a
lower bound on the effort (in terms of expected number of samples)
required to achieve a certain confidence level. And a problem that
requires a larger effort can be described as more complex. Indeed, in
the case of fixed confidence problems, Kaufmann et al. (2016) describe
problems as having a larger \emph{sampling complexity}.

Following Kaufmann et al. (2016), we can now define the complexity
\(\kappa_C(\nu)\) for the fixed confidence setting as

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \lim_{\delta \to 0} \sup \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
\end{equation}

This definition makes sense if we consider the fact that the confidence
level \(\delta\) is experimenter chosen and thus not relevant in
describing the complexity. Thus, by including \(\log(1/\delta)\)
explicitly in \eqref{eq:KappaC}, we get rid of the confidence term in
the lower bound on \(\mathbb{E}_{\nu}[T]\) after plugging it into
\eqref{eq:KappaC}. We arrive at the lower bound on the complexity
measure given in Kaufmann et al. (2016):

@@

Given this description, we would expect that a complexity measure in a
fixed confidence thresholding bandit probem might involve replacing
\(\mu_{[m]}\) and \(\mu_{[m+1]}\) by the actual threshold \(\tau\) that
divides the group above the threshold from the group below the
threshold.

However, given the problem formulation in Locatelli et al. (2016), we
are mainly interested in complexity measures and algorithms for the
fixed budget setting. As we will see now, the results of Kaufmann et al.
(2016) are more limited for this case. While the authors are able to
provide a bound on their complexity measure in the fixed budget case, it
only applies to the case of \emph{two-armed} bandit models. Consider a
consistent fixed budget strategy \(\mathcal{A}\) (\(p_t(\nu)\) tends to
zero as \(t \rightarrow \infty\)), and define the complexity in the
fixed budget setting as follows:

@@

While we included the experimenter-fixed \(\delta\) in the definition of
\(\kappa_C\), we now include the experimenter-fixed \(T\) in the
definition of \(\kappa_B\) to disregard it in the complexity measure
after plugging in the lower bound on \(p_t(\nu)\). The resulting lower
bound given in Theorem 12 of Kaufmann et al. (2016):

\begin{theorem}[Theorem 12, Kaufmann et al., 2016] \label{theorem:KaufmannEtAlTheorem12}
Let $\nu = (\nu_1, \nu_2)$ be a two-armed bandit model such that $\mu_1 > \mu_2$. In the fixed budget setting, any consistent algorithm satisfies:

@@

For a proof, consider first the two different bandit models, \(\nu\) and
\(\nu'\), where we fix w.l.o.g. \(a^* = 1\) as the best arm in \(\nu\),
while \(a^* = 2\) in \(\nu'\). Note that in this case we don't
necessarily try to fool the algorithm by a change of distribution.
Indeed, we want the algorithm \(\mathcal{A}\) to be consistent for both
problems. Since we are in the fixed budget setting, the stopping time is
fixed at \(T = t\). Even though the correct decision differs between the
two problems, we focus on the event \(A = (\hat{S}_1 = 1)\). Now, we can
apply Lemma 1 as before, as it in essence gives a measure of how
different two bandit models are. Here, we want to know how different
\(\nu\) is from \(\nu'\), and so, given we have only two arms,

@@

The expectations were chosen with respect to \(\nu'\) in order to allow
for the following: We have \(p_t(\nu) = 1 - \mathbb{P}_{\nu}(A)\) and
\(p_t(\nu') = \mathbb{P}_{\nu'}(A)\) (since \(A\) is wrong in \(\nu'\)).
But since algorithm \(\mathcal{A}\) is consistent for both \(\nu\) and
\(\nu'\), we know that there should exist some number of samples such
that the probability of event \(A\) is bigger in setting \(\nu\) (where
it is the correct decision) than in setting \(\nu'\) (where this would
be a wrong decision and failure). Thus, for every \(\epsilon > 0\),
there exists \(t_0(\epsilon)\) such that for all
\(t \geq t_0(\epsilon)\),
\(\mathbb{P}_{\nu'}(A) \leq \epsilon \leq \mathbb{P}_\nu(A)\).
Consequently, if we plug in the bound of \(\epsilon\) for
\(\mathbb{P}_{\nu'}(A)\), then

@@

As noted by Kaufmann et al. (2016), the advantage of this lower bound is
that it makes the complexity in the fixed confidence and the fixed
budget setting directly comparable. The disadvantage of course being
that the result only holds for two-armed models. While the authors are
not able to derive directly comparable lower bounds for the top-\(m\)
case, they derive a first lower bound in the Gaussian case with equal
variances, which we describe shortly in the appendix in
\autoref{sec:KaufmannLBTopMGaussian}.

Before we discuss the strategies of Kaufmann et al. (2016) matching the
lower bounds, we now show how lower bounds can be derived very similarly
for the fixed budget thresholding problem.

\subsubsection{Lower Bound for Fixed Budget Thresholding
Problem}\label{lower-bound-for-fixed-budget-thresholding-problem}

In order to derive a bound for the fixed budget problem, Kaufmann et al.
(2016) have focused on the case of the two-armed bandit which is the
most simple version of the top-\(m\) problem. Less than two arms do not
make sense, since then this single arm will always be the best arm. In
the case of the thresholding bandit, however, a single-armed problem
makes still some sense in that we still have to classify this arm
correctly with respect to the threshold. Thus, we can show the following
corollary which gives the a bound on the complexity of the single-armed
thresholding bandit.

\begin{corollary}
Let $\nu = \nu_1$ be a one-armed thresholding bandit model where $\tau$ is the threshold fixed upfront. Let $\nu$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_1$, and the Kullback-Leibler divergence between distributions $\nu_1$ and $\nu_1'$ can be written as $\KL(\nu_1', \nu_1) = \KL(\mu_1', \mu_1)$. In the fixed budget setting, any consistent algorithm satisfies:

$$
\lim_{t \rightarrow \infty}- \frac{1}{t} \log p_t(\nu) \leq \KL(\tau, \mu_1)
$$
\end{corollary}

This of course is basically the Chernoff-Stein Lemma for the hypothesis
test of two alternatives (compare chapter 11 in Cover and Thomas, 2006).

But as we see in the following corollary, we can extend the lower bound
to the \(K\)-armed fixed budget thresholding bandit problem, which
stands in contrast to the fact that for the top-\(m\) problem, it is
only possible to show the lower bound for two arms.

\begin{corollary}
Let $\nu = (\nu_1, ..., \nu_K)$ be a $K$-armed thresholding bandit problem in which $\tau$ is the threshold fixed upfront. For $i \in \{1,...,K\}$, let $\nu_i$ be from the univariate canonical exponential family of distributions such that it can be parameterized by its mean, $\mu_i$, and the Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_i'$ can be written as $\KL(\nu_i, \nu_i') = \KL(\mu_i, \mu_i')$. In the fixed budget setting, every consistent algorithm satisfies:

$$
\lim_{t \rightarrow \infty} -\frac{1}{t} \log p_t(\nu) \leq \max_{a \in \{1,...,K\}} \KL(\tau, \mu_a)
$$
\end{corollary}

Given the lower bounds on the sampling complexity and error probability,
as well as the complexity measures, we now turn to sampling strategies
that are designed to match these lower bounds.

@@

Kaufmann et al. (2016) do not present algorithms matching the lower
bound of Theorem \ref{theorem:KaufmannEtAlTheorem17}. They do consider
algorithms that connect to Theorem \ref{theorem:KaufmannEtAlTheorem4}
and Theorem \ref{theorem:KaufmannEtAlTheorem12}. Given that we aim to
extend the fixed budget thresholding bandit problem, we are most
interested in the matching strategies for Theorem
\ref{theorem:KaufmannEtAlTheorem12}. However, given that this lower
bound applies only to two-armed bandits, the algorithms proposed by
Kaufmann et al. (2016) are of limited practical interest. Furthermore,
the proposed strategies require knowledge that is in general not
available upfront: For Gaussian distributions, the knowledge of the
(potentially different) variance is assumed which enables a strategy
that pulls each arm proportional to its variance.

Even more difficult are the assumptions in the case of Bernoulli
two-armed bandit models: The proposed algorithm requires knowledge about
the true parameters of the distributions. That this limits the practical
interest is also noted by the authors of Kaufmann et al. (2016). Thus,
they suggest to use uniform sampling strategies in the case of two-armed
Bernoulli bandits, and show that there is not much to be lost by doing
so.

Thus, Kaufmann et al. (2016) join a number of other papers like Audibert
et al. (2010) and Kaufmann and Kalyanakrishnan (2013) which struggle to
find matching strategies in the fixed budget setting that do not rely on
knowledge of parameters or the complexity of the problem.

In contrast, Kaufmann et al. (2016) are able to show that their
complexity measure derived for the fixed confidence setting,
\(\kappa_C(\nu)\), can be upper-bounded using the upper bound given for
the KL-LUCB algorithm in Kaufmann and Kalyanakrishnan (2013).
Consequently, in the case of exponential family bandits, the complexity
\(\kappa_C(\nu)\) is bounded as given in equation (6) in Kaufmann et al.
(2016):

@@

\subsection{\texorpdfstring{Optimal Best Arm Identification
\label{sec:OptimalBestArmIdentification}}{Optimal Best Arm Identification }}\label{optimal-best-arm-identification}

Instead of discussing the KL-LUCB algorithm for the fixed confidence
top-\(m\) problem, we shift our focus slightly onto the fixed confidence
best arm identification problem, which is discussed in Garivier and
Kaufmann (2016). The authors derive again a lower bound on the sample
complexity using again the Lemma \autoref{theorem:KaufmannEtAlLemma1}.
Furthermore, they propose a matching strategy for \(K \geq 2\) arms.

The setting differs slightly from the setting considered in Kaufmann et
al. (2016). In particular, Garivier and Kaufmann (2016) focus on
distributions \(\nu_{\theta}\) from the univariate canonical exponential
family of distributions, which can be parameterized by their mean
\(\stackrel{.}{b}(\theta) = \mu\), and thus can be written as
\(\nu^{\mu}\); for these, we write the Kullback-Leibler divergence as
(compare \autoref{sec:LRforUnivariateExponentialFamily} and Cappé et
al., 2013)

\begin{equation*}
\KL(\mu, \mu') = \KL(\nu_{\mu},\nu_{\mu'}) = \KL(\nu_{\theta},\nu_{\theta'}) = \KL(\nu, \nu').
\end{equation*}

Furthermore, if we let \(\mathcal{S}\) to be a set of bandit models with
\(K\) distributions each, then each model is fully defined by a vector
\(\bm{\mu} = (\mu_1, \dots, \mu_K)\). Assume that every
\(\bm{\mu} \in \mathcal{S}\) has a unique maximum given by
\(a^*(\bm{\mu})\) such that
\(\mu_{a^*} > \max_{a \neq a^*(\bm{\mu})} \mu_a\). In order to fix the
confidence, we specify the risk \(\delta\). Similar to the top-\(m\)
case considered before, strategies corresponding to this risk are called
\(\delta\)-PAC if for every \(\bm{\mu} \in \mathcal{S}\), the strategy
ends surely after a finite number of samples,
\(\mathbb{P}_{\bm{\mu}}(T_{\delta} < \infty) = 1\), and the error
probability is at least as small as the fixed risk level,
\(\mathbb{P}_{\bm{\mu}}(\hat{a}_{T_{\delta}} \neq a^*) \leq \delta\). In
order to derive the lower bound on the expected number of samples
\(\mathbb{E}[T]\) through a change in distributions, we introduce the
set of problems for which the optimal arm is different from
\(\bm{\mu}\):

@@

where \(\bm{\lambda}\) is the vector of means defining the distributions
of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
probability distributions on the arms \(\{1,...,K\}\):
\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). Each
\(w_i\) corresponds to the fraction of overall samples that the arm
\(i\) receives. We are now ready to state the lower bound:

@@

\begin{equation*}
\mathbb{E}_{\bm{\mu}} [T_{\delta}] \geq T^*(\bm{\mu}) \text{\em{d}}(\delta,1-\delta),
\end{equation*}

@@

We show empirically that part of this problem can be alleviated by
including the D-Tracking rule proposed by Garivier and Kaufmann (2016)
and discussed in \autoref{sec:OptimalBestArmIdentification} into the SLR
algorithm.

@@

{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-1-1}
